---
title: "COVID-19 in Malaysia — Data Visualisations"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar:
        - {icon: "fa-github", href: "https://github.com/fyii200", align:  right}
        - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/fabian-yii-15413016a/", align: right}
---

```{r setup, include=FALSE}
## load relevant functions, packages ##
# install.packages("waffle", repos = "https://cinc.rud.is")
# install.packages("plotly")
# install.packages('dplyr')

library(RColorBrewer)
library(waffle)
library(dplyr)
source('functions/data_update.R')

### DAILY CASES, TESTS, DEATHS, etc. ###
## read raw data (worldwide) and configure data frame named 'mys'
#world<-read.csv('https://covid.ourworldindata.org/data/owid-covid-data.csv')
# mys <- world[which(world$iso_code=='MYS'),]
mys <- read.csv('data/mys.csv'); mys <- mys[,-1]
# update data!
mys <- data_update(mys)
mys$date <- as.Date(mys$date)

### VACCINATION DATA ###
# data <- 'https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/country_data/Malaysia.csv'
# d$date <- as.Date(d$date)
data <- 'data/vaccine.csv'
d <- read.csv(data); d<-d[,-1]
d$date <- as.Date(d$date, '%d/%m/%Y')
```

Daily summary {data-icon="fa-table"}
=========================================


Row {data-height=420, .tabset}
-----------------------------------------
### Cases
```{r include=FALSE}
source('cases/daily_new_cases.R')
label <- paste(format(weekchange*7, scientific=F, big.mark=','), 
               ' (', weekchange_perc, '%)', sep='')
```

<span style="font-size:1.5em;"> **People tested positive** </span>

Daily <span style="font-size:1em; color:grey;"> *`r format(max(x, na.rm=T), '%d %b %Y')`*</span>  
<span style="font-size:2.5em"> **+`r dailynew`** </span>

7-day total <span style="font-size:1em; color:grey;"> *(week ending `r lastlastdate`)*</span>  
<span style="font-size:1.5em"> **`r format(sum(lastlast7cases), scientific=F, big.mark=',')`** </span>

7-day total <span style="font-size:1em; color:grey;"> *(week ending `r format(max(x), '%d %b')`)*</span>  
<span style="font-size:1.5em"> **`r format(sum(last7cases), scientific=F, big.mark=',')`** </span> &nbsp;
<span style="font-size:1.1em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

```{r echo=FALSE, fig.width=7.5, fig.height=4}
# make empty plot then add smoothed line
plot(x, y, xaxt='n', yaxt='n', bty='n', type='n', xlab='', ylab='')
par(las=0)
axis(side=1, labels=format(xtlab, '%b %Y'), at=xtlab, 
    tick=F, col.axis='gray56', cex.axis=0.9)
lines(x, mys$new_cases_smoothed, col=col[2], lwd=4)
```



### Testing
```{r include=FALSE}
source('cases/daily_tests.R')
```

<span style="font-size:1.5em;"> **COVID-19 tests conducted** </span>

Daily <span style="font-size:1em; color:grey;"> *`r format(latest_date, '%d %b %Y')`*</span>  
<span style="font-size:2.5em"> **`r latest_tests`** </span>

7-day average <span style="font-size:1em; color:grey;"> *(week ending `r format(max(lastlast7$date), '%d %b')`)*</span>  
<span style="font-size:1.5em"> **`r format(lastlast7avg, scientific=F, big.mark=',')`** </span>

7-day average <span style="font-size:1em; color:grey;"> *(week ending `r format(latest_date, '%d %b')`)*</span>  
<span style="font-size:1.5em"> **`r format(last7avg, scientific=F, big.mark=',')`** </span>
<span style="font-size:1.1em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

```{r echo=FALSE, fig.width=7.5, fig.height=4}
# make empty plot then add smoothed line
plot(test.s$x, test.s$y, xaxt='n', yaxt='n', bty='n', type='n', xlab='', ylab='')
par(las=0)
axis(side=1, labels=format(xtlab, '%b %Y'), at=xtlab, 
    tick=F, col.axis='gray56', cex.axis=0.9)
lines(test.s$x, test.s$y, lwd=4, col=col[2])
```



### Deaths
```{r include=FALSE}
source('deaths/daily_deaths.R')
```

<span style="font-size:1.5em;"> **Reported deaths** </span>

Daily <span style="font-size:1em; color:grey;"> *`r format(max(x, na.rm=T), '%d %b %Y')`*</span>  
<span style="font-size:2.5em"> **`r y[length(y)]`** </span>

7-day average <span style="font-size:1em; color:grey;"> *(week ending `r format(max(x), '%d %b')`)*</span>  
<span style="font-size:1.5em"> **`r format(death7avg, scientific=F, big.mark=',')`** </span>

7-day average <span style="font-size:1em; color:grey;"> *(week ending `r lastdeath7avg_date`)*</span>  
<span style="font-size:1.5em"> **`r format(lastdeath7avg, scientific=F, big.mark=',')`** </span>
<span style="font-size:1.1em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

```{r echo=FALSE, fig.width=7.5, fig.height=4}
# make empty plot then add smoothed line
plot(x, y.s, xaxt='n', yaxt='n', bty='n', type='n', xlab='', ylab='')
par(las=0)
axis(side=1, labels=format(xtlab, '%b %Y'), at=xtlab, 
    tick=F, col.axis='gray56', cex.axis=0.9)
lines(x, y.s, lwd=4, col=col[2])
```




Row {data-height=350}
-----------------------------------------

### Vaccinations - Daily
```{r include=FALSE}
source('vaccinations/daily_new_doses.R')
col <- brewer.pal(9,'Blues')[c(5,8)]   
```
<span style="font-size:1.5em;"> **People vaccinated ** </span>
<span style="color:grey;"> *`r format(max(x), '%d %b %Y')`*</span> 

<span style="font-size:1em;">New 1st dose </span> </span>  
<span style="font-size:2.5em; color:`r col[1]`;"> **+`r new.y1`** </span>
 
 
<span style="font-size:1em;">New 2nd dose </span> </span>  
<span style="font-size:2.5em; color:`r col[2]`;"> **+`r new.y2`** </span>
  
   
### Vaccinations - Cumulative total
```{r include=FALSE}
source('vaccinations/cumulative_doses.R')
```
<span style="font-size:1.5em;"> **Total ** </span>
<span style="color:grey;"> *up to & including `r format(max(x), '%d %b %Y')`*</span>

<span style="font-size:1em;"> 1st dose </span> </span>  
<span style="font-size:2.5em; color:`r col[3]`;"> **`r format(max(y1, na.rm=T), scientific=F, big.mark=',')`** </span>

<span style="font-size:1em;"> 2nd dose </span> </span>  
<span style="font-size:2.5em; color:`r col[2]`;"> **`r format(max(y2, na.rm=T), scientific=F, big.mark=',')`** </span>


### % minimum target Population (23.2m) vaccinated
```{r echo=FALSE}
source('summary/squareplot.R')
```







Cases {.storyboard data-icon="fa-vial" fig_mobile=TRUE}
=========================================


### <span style="font-size:1em;"> **Daily New Cases** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('cases/daily_new_cases.R')
```

*** 
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`* 

_____________________

<span style="font-size:4.5em; color:`r col[1]`;"> **+`r dailynew`** </span>  
<span style="color:grey;"> *new cases in the past 24 hours.* </span>

_____________________

<span style="font-size:2.5em; color:`r col[2]`;"> **`r weeknew`** </span> <span style="font-size:1.1em; color:grey;"> **cases / day** </span> 
 
<span style="color:grey;"> *7-day average for the week ending `r format(max(x, na.rm=T), '%d %b')`.* </span>


<span style="font-size:2.5em; color:`r col[2]`;"> **`r lastweeknew`** </span> <span style="font-size:1.1em; color:grey;"> **cases / day** </span> 
 
<span style="color:grey;"> *7-day average for the week ending `r lastlastdate`.* </span>

<span style="font-size:1.5em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Daily COVID-19 Tests** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('cases/daily_tests.R')
```

*** 
*Latest data provided on `r format(max(test$x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:4em; color:`r col[2]`;"> **`r latest_tests`** </span>  
<span style="color:grey;"> *tests were done in a day.* </span>   

<span style="font-size:3em; color:red;"> **`r pos_case`** </span>  
<span style="color:grey;"> *positive cases were reported on the same day.* </span>

_____________________

<span style="font-size:2em; color:`r col[2]`;"> **`r format(last7avg, scientific=F, big.mark=',')`** </span> <span style="font-size:1em; color:`r col[2]`;"> **tests / day** </span>

<span style="color:grey;"> *7-day average for the week ending `r format(max(last7$date, na.rm=T), '%d %b')`.* </span> 

<span style="font-size:2em; color:`r col[2]`;"> **`r format(lastlast7avg, scientific=F, big.mark=',')`** </span> <span style="font-size:1em; color:`r col[2]`;"> **tests / day** </span>

<span style="color:grey;"> *7-day average for the week ending `r format(max(lastlast7$date, na.rm=T), '%d %b')`.* </span>

<span style="font-size:1.5em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Positivity Rate** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('cases/positivity_rate.R')
```

*** 
*Latest data provided on `r format(mys$date[length(pos)], '%d %B %Y')`*   

_____________________

<span style="font-size:5em; color:red;"> **`r latest_pr`%** </span>  
<span style="color:grey;"> *Daily positivity rate.* </span>   

<span style="font-size:3em; color:red;"> **`r pos7avg`%** </span>  
<span style="color:grey;"> *7-day moving average of positivity rate.* </span>

_____________________


<span style="color: Grey;"> *Positivity rate is equal to the number of positive tests, i.e., tests that come back positive, divided by the total number of tests conducted (PCR & antigen rapid tests) within the past 24 hours. [As a general rule of thumb](https://www.jhsph.edu/covid-19/articles/covid-19-testing-understanding-the-percent-positive.html), positivity rate of **less than 5%** means there's an adequate level of testing relative to the size of the outbreak, or the epidemic is under control in a country.* </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Cumulative Cases** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('cases/cumulative_cases.R')
```

***
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:3.5em; color:`r col[2]`;"> **`r format(max(y, na.rm=T), scientific=F, big.mark=',')`** </span>  
<span style="color:grey;"> *Cumulative number of cases.* </span>

_____________________

<span style="font-size:2em; color:`r col[2]`;"> **`r format(round(max(mys$total_cases_per_million), 0), scientific=F, big.mark=',')`** </span>  
<span style="color:grey;"> *reported cases per million population.* </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*







Deaths {.storyboard data-icon="fa-skull"}
=========================================

### <span style="font-size:1em;"> **Daily Deaths** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
source('deaths/daily_deaths.R')
```

***
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:5em; color:`r col[2]`;"> **+`r death7avg`** </span>  
<span style="color:grey;"> *deaths were reported.* </span>

_____________________

<span style="font-size:2.5em; color:`r col[2]`;"> **`r death7avg`** </span> <span style="font-size:1.1em; color:grey;"> **deaths / day** </span> 
 
<span style="color:grey;"> *7-day average for the week ending `r format(max(x, na.rm=T), '%d %b')`.* </span>


<span style="font-size:2.5em; color:`r col[2]`;"> **`r lastdeath7avg`** </span> <span style="font-size:1.1em; color:grey;"> **deaths / day** </span> 
 
<span style="color:grey;"> *7-day average for the week ending `r lastdeath7avg_date`.* </span>

<span style="font-size:1.5em; color:`r arrowcol`;"> **`r ifelse(weekchange>=0, print('⬆'), print('⬇'))`  `r label`**</span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Case Fatality Ratio** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
source('deaths/case_fatality_rate.R')
```

***
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:5em; color:`r col[2]`;"> **`r cfr`%** </span>  
<span style="color:grey;"> *Case Fatality Ratio (CFR) or more commonly known as Case Fatality Rate.* </span>

_____________________

<span style="color: Grey;"> *[CFR](https://www.who.int/news-room/commentaries/detail/estimating-mortality-from-covid-19) is the total number of deaths divided by the total number of confirmed cases. Despite being a commonly used measure of mortality from a disease, it has a number of important limitations and underlying assumptions which call for careful interpretation, especially during a fast-moving pandemic. Read [here](https://ourworldindata.org/covid-mortality-risk) for instance.* </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Cumulative Deaths** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
source('deaths/cumulative_deaths.R')
```

***
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="color:`r col[2]`; font-size:4.5em;">**`r cum_deaths`**</span> 

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*







Vaccinations {.storyboard data-icon="fa-syringe"}
=========================================


### <span style="font-size:1em;"> **Percentage Vaccinated** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('vaccinations/percentage_vaccinated.R')
```

*** 
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:4.5em; color:`r col[3]`;"> **`r round(max(y1), 1)`%** </span>  
<span style="color:grey;"> *have received at least 1 dose of a vaccine.* </span>

<span style="font-size:1.2em; color:`r col[3]`;"> **+ `r inc1`%** </span>  
<span style="color:grey;"> *from `r format(d$date[length(d$date)-1], '%d %b')`* </span>

_____________________  

<span style="font-size:4.5em; color:`r col[2]`;"> **`r round(max(y2), 1)`%** </span>  
<span style="color:grey;"> *have received at least 2 doses of a vaccine.* </span>  

<span style="font-size:1.2em; color:`r col[2]`;"> **+ `r inc2`%** </span>  
<span style="color:grey;"> *from `r format(d$date[length(d$date)-1], '%d %b')`* </span>

_____________________

<div style="text-align:left;"> <span style="color:Grey;"> *Based on [2020 population estimates](https://www.dosm.gov.my/v1/index.php?r=column/cthemeByCat&cat=155&bul_id=OVByWjg5YkQ3MWFZRTN5bDJiaEVhZz09&menu_id=L0pheU43NWJwRWVSZklWdzQ4TlhUUT09) of 32.7 million (citizens & non-citizens).* </span>  

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Cumulative Doses** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('vaccinations/cumulative_doses.R')
```

*** 
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*  

_____________________

<span style="font-size:3.5em; color:`r col[3]`;"> **`r format(max(y1), scientific=F, big.mark=',')`** </span>  
<span style="color:grey;"> *first doses have been administered.* </span>

_____________________  

<span style="font-size:3.5em; color:`r col[2]`;"> **`r format(max(y2), scientific=F, big.mark=',')`** </span>  
<span style="color:grey;"> *second doses have been administered.* </span>  

_____________________

<span style="color: grey;"> Vaccine portfolio: Pfizer-BioNTech, Sinovac, Oxford-AstraZeneca </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Daily New Doses** </span> 
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('vaccinations/daily_new_doses.R')
```

*** 
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:4em; color:`r col[1]`;"> **+ `r new.y1`** </span>  
<span style="color:grey;"> *new doses from `r format(x[length(x)-1], '%d %b')`.* </span>

<span style="font-size:4em; color:`r col[2]`;"> **+ `r new.y2`** </span>  
<span style="color:grey;"> *new doses from `r format(x[length(x)-1], '%d %b')`.* </span>

_____________________

<span style="font-size:2.5em; color:`r col[1]`;"> **+`r format(week.y1, scientific=F, big.mark=',')`**</span>
<span style="color:`r arrowcol_y1`;"> **`r ifelse(weekchange_y1>=0, print('⬆'), print('⬇'))`  `r label_y1`**</span>  

<span style="color:grey;"> *each day on average over the past seven days* </span>

<span style="font-size:2.5em; color:`r col[2]`;"> **+`r format(week.y2, scientific=F, big.mark=',')`**</span>
<span style="color:`r arrowcol_y2`;"> **`r ifelse(weekchange_y2>=0, print('⬆'), print('⬇'))`  `r label_y2`**</span> 

<span style="color:grey;"> *each day on average over the past seven days* </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*



### <span style="font-size:1em;"> **Progress Tracker** </span>
```{r echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
# source code file for the plot
source('vaccinations/progress_tracker.R')
```

*** 
*Latest data provided on `r format(max(x, na.rm=T), '%d %B %Y')`*   

_____________________

<span style="font-size:4em; color:`r col[3]`;"> **`r dailydose1`** </span>
<span style="color:grey;"> *first doses* </span>  

<span style="font-size:4em; color:`r col[2]`;"> **`r dailydose2`** </span>
<span style="color:grey;"> *second doses* </span>  

<span style="color:grey;"> *required **each day on average** over the next **`r dayleft`** days to achieve Phase 2 target.* </span>  

_____________________

<span style="color: Grey;"> *[The government aims](https://www.vaksincovid.gov.my/pdf/Program_Imunisasi_COVID-19_Kebangsaan_Versi_Bahasa_Inggeris.pdf) to vaccinate at least 23.6 million people (72.2% of population) against COVID-19 by February 2022. Phase 1, 2 & 3 involve 0.5m, 9.4m & at least 13.7m people, respectively. Dates shown denote the end of each of the 3 vaccination phases.* </span>

_____________________
*Last updated on `r format(Sys.Date(), '%d %b %Y')`*
