---
title: "COVID-19 in Malaysia"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 3
    orientation: rows
    navbar:
          - {title: "About me", icon: "fa-github", href: "https://github.com/fyii200", align: right}
    social: menu
    fig_mobile: FALSE
date: <span style="font-size:0.8em;">`r format(Sys.Date(), '%d %b %Y')` </span>
---

```{r setup, include=FALSE}
## load relevant functions, packages ##
# install.packages("waffle", repos = "https://cinc.rud.is")
# install.packages('dygraph')
# install.packages('dplyr)
library(RColorBrewer)
library(highcharter)
library(dplyr)
library(waffle)
library(xts)

### DAILY CASES, TESTS, DEATHS, etc. ###
## read raw data (worldwide) and configure data frame named 'mys'
world     <- read.csv('https://covid.ourworldindata.org/data/owid-covid-data.csv')
mys       <- world[which(world$iso_code == 'MYS'), ]
mys$date  <- as.Date(mys$date)

### VACCINATION DATA ###
# data    <- 'https://raw.githubusercontent.com/owid/covid-19-data/master/public/data/vaccinations/country_data/Malaysia.csv'
data      <- 'data/vaccine.csv'
d         <- read.csv(data); d<-d[,-1]
d$date    <- as.Date(d$date, '%d/%m/%Y')

## source all functions & computations ##
source('computations.R')
```


Daily summary {data-icon="fa-table"}
=========================================

Row {data-height=300}
-----------------------------------------

### Vaccinations - Daily Total & Cumulative Total {.no-mobile}
<span style="font-size:1.5em;"> **People vaccinated ** </span>
<span style="font-size:0.9em; color:grey;"> *up to & including `r format(max(x), '%d %b %Y')`*</span> 

<span style="font-size:1em;"> 1st dose | </span> <span style="font-size:0.9em; color:grey;"> &nbsp; cumulative total </span>  
<span style="font-size:2em; color:`r vac_col[1]`;"> **+`r latest_dose1_formatted`** </span> <span style="font-size:2.5em;"> | </span> &nbsp;
<span style="font-size:1.5em; color:`r vac_col[1]`;"> **`r cumul_dose1_formatted`** </span>
 
 
<span style="font-size:1em;"> 2nd dose | </span> <span style="font-size:0.9em; color:grey;"> &nbsp; cumulative total </span>  
<span style="font-size:2em; color:`r vac_col[2]`;"> **+`r latest_dose2_formatted`** </span> <span style="font-size:2.5em;"> | </span> &nbsp;
<span style="font-size:1.5em; color:`r vac_col[2]`;"> **`r cumul_dose2_formatted`** </span>


### Vaccinations - Daily Total & Cumulative Total {.mobile}
<span style="font-size:1.5em;"> **People vaccinated ** </span>
<span style="font-size:0.9em; color:grey;"> *up to `r latest_dose_date`*</span> 

<span style="font-size:1em;"> 1st dose | </span> <span style="font-size:0.9em; color:grey;"> &nbsp; cumulative total </span>  
<span style="font-size:2em; color:`r vac_col[1]`;"> **+`r latest_dose1_formatted`** </span> <span style="font-size:2.5em;"> | </span> &nbsp;
<span style="font-size:1.2em; color:`r vac_col[1]`;"> **`r cumul_dose1_formatted`** </span>
 
 
<span style="font-size:1em;"> 2nd dose | </span> <span style="font-size:0.9em; color:grey;"> &nbsp; cumulative total </span>  
<span style="font-size:2em; color:`r vac_col[2]`;"> **+`r latest_dose2_formatted`** </span> <span style="font-size:2.5em;"> | </span> &nbsp;
<span style="font-size:1.2em; color:`r vac_col[2]`;"> **`r cumul_dose2_formatted`** </span>


### At least 1 dose — rounded percentage of population
```{r echo=FALSE}
plot_square(dataset = target, 
            rows = c(1, 3, 5), 
            color = col[1] ) %>%
hc_legend(enabled = FALSE)
```



Row {data-height=450}
-----------------------------------------

### Cases
<span style="font-size:1.5em;"> **People tested positive** </span>

Daily <span style="font-size:0.9em; color:grey;"> *`r latest_date`*</span>  
<span style="font-size:1.5em"> **+`r new_cases`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r cases_last_7day_date_formatted` )*</span>  
<span style="font-size:1.3em"> **`r cases_last_7day_avg_formatted`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r latest_date` )*</span>  
<span style="font-size:1.3em"> **`r cases_7day_avg_formatted`** </span> &nbsp;
<span style="font-size:1em; color:`r cases_arrowcol`;"> **`r ifelse( cases_week_change >= 0, print('▲'), print('▲'))`  `r cases_label`**</span>

#### 
```{r echo=FALSE, fig.width=3.5, fig.height=1}
plot_line(mys$date, mys$new_cases_smoothed, case_col)
```


### Testing
<span style="font-size:1.5em;"> **COVID-19 tests conducted** </span>

Daily <span style="font-size:0.9em; color:grey;"> *`r tests_7day_date_formatted`*</span>  
<span style="font-size:1.5em"> **`r latest_tests`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r tests_last_7day_date_formatted`)*</span>  
<span style="font-size:1.3em"> **`r tests_last_7day_avg_formatted`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r tests_7day_date_formatted`)*</span>  
<span style="font-size:1.3em"> **`r tests_7day_avg_formatted`** </span>
<span style="font-size:1em; color:`r tests_arrowcol`;"> **`r ifelse(tests_week_change >= 0, print('▲'), print('▼'))`  `r tests_label`**</span>

#### 
```{r echo=FALSE, fig.width=3.5, fig.height=1}
plot_line(mys$date, mys$new_tests_smoothed, test_col[1])
```


### Deaths
<span style="font-size:1.5em;"> **Reported deaths** </span>

Daily <span style="font-size:0.9em; color:grey;"> *`r latest_date`*</span>  
<span style="font-size:1.5em"> **`r new_deaths`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r deaths_last_7day_date_formatted`)*</span>  
<span style="font-size:1.3em"> **`r deaths_last_7day_avg`** </span>

7-day average <span style="font-size:0.8em; color:grey;"> *(week ending `r latest_date`)* </span>  
<span style="font-size:1.3em"> **`r deaths_7day_avg`** </span> <span style="font-size:1em; color:`r deaths_arrowcol`;"> **`r ifelse(deaths_week_change >= 0, print('▲'), print('▼'))`  `r deaths_label`**</span>

#### 
```{r echo=FALSE, fig.width=3.5, fig.height=1}
# make empty plot then add smoothed line
plot_line(mys$date, mys$new_deaths_smoothed, death_col)
```



Guide {data-icon="fa-question-circle"}
=========================================

Row {data-height=100}
-----------------------------------------
### <span style="font-size:1.8em;"> Interact with the graphs! </span>
Data are updated daily whenever they become available (date printed on the navigation bar shows when the data were last updated). All graphs (except the few trend lines on the 'Daily summary' homepage ) on this site are **interactive**. Here are a few tips to help you make the most of these graphs.

<span style="color:Navy; font-size:1em;"> **First** </span>, view the graphs on a **computer screen** whenever possible. You will be able to <span style="color:Navy; font-size:1em;"> **hover your cursor over each graph (mouseover)** </span> to display the tooltip text containing the y-value (e.g., number of vaccinations each day) corresponding to a specific date. On a **touch device**, <span style="color:Navy; font-size:1em;"> </span> the tooltip text will be displayed and updated when the **finger moves across the graph**. </span>

<span style="color:Navy; font-size:1em;"> **Second**,</span> you'll notice a <span style="color:Navy; font-size:1em;"> **horizontal scrollbar** </span> just underneath the x-axis of each graph. Use it to specify the <span style="color:Navy; font-size:1em;"> **date range** </span> to zoom in and out of the graph. Alternatively, you can click or tap on the range selector buttons to select some pre-configured ranges. More functions and graphs may be added in the near future so keep checking back. 

If you're interested in my work and wish to connect with me, or if you have any queries or suggestions, you can contact me through several means (click [here](https://github.com/fyii200) or 'About me' to go to my GitHub page; contact details are listed there). Happy exploring!  

________________________

#### <span style="font-size:1em;"> Data sources </span>
All data pertinent to vaccinations: *The Special Committee for Ensuring Access to COVID-19 Vaccine Supply [(JKJAV)](https://www.vaksincovid.gov.my/en/about-jkjav/)* 

Other data: *Hasell, J., Mathieu, E., Beltekian, D. et al. A cross-country database of COVID-19 testing. Sci Data 7, 345 (2020). https://doi.org/10.1038/s41597-020-00688-8*

________________________



Cases {.storyboard data-icon="fa-vial"}
=========================================


### <span style="font-size:1.3em;"> **Daily New Cases |** </span> <br> <span style="font-size:0.9em;"> How many new cases are being confirmed each day? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(mys, select = c(date, new_cases, new_cases_smoothed) )

names(data)[ c(2, 3) ] <- c("Daily cases", "7-day avg")

data$`7-day avg` <- round(data$`7-day avg`, 0)

# convert data frame into xts format
data <- xts(data[, 2:3], order.by = data$date) 

col<-brewer.pal(9, 'Oranges')[c(4,8)]

# Plot!
config_hc(data$`Daily cases`, 
          'area', 
          'Daily new cases', 
          col[1], 
          '')                       %>%
  
hc_add_series(data$`7-day avg`, 
              type = 'line',  
              name = '7-day avg', 
              color = col[2])
```

***
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_date`* </span>

<span style="font-size:1.5em; color:`r col[2]`;"> **+`r new_cases`** </span>  
<span style="color:grey;"> *new cases in the past 24 hours.* </span>


### <span style="font-size:1.3em;"> **Daily Tests |** </span> <br> <span style="font-size:0.9em;"> Are we doing enough of COVID-19 testing? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(mys, select = c(date, new_tests_smoothed, new_cases_smoothed) )

names(data)[ c(2, 3) ] <- c("All tests", "Positive")

data$Positive <- round(data$Positive, 0)

# remove rows where testing data are not available
data <- data[ complete.cases(data), ]

# convert data frame into xts format
data <- xts(data[, 2:3], order.by = data$date)         

# col [1] for all tests [2] for positive tests
col <- brewer.pal(11, 'RdYlBu')[ c(9, 1) ]

# Plot!
config_hc(data$`All tests`, 
          'area', 
          'All tests', 
          col[1], 
          '')                            %>%

hc_add_series(data$Positive, 
              type = 'area',  
              name = 'Positive tests', 
              color = col[2])            %>%
  
hc_subtitle(text = 'Based on 7-day average')
```

*** 
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r tests_7day_date_formatted`* </span>   

<span style="font-size:1.5em; color:`r test_col[1]`;"> **`r tests_7day_avg_formatted`** </span>  
<span style="color:grey;"> *tests were done per day on average over the past week.* </span>   

<span style="font-size:1.5em; color:`r test_col[2]`;"> **`r pos_tests_formatted`** </span>  
<span style="color:grey;"> *positive cases were reported per day on average over the same week.* </span>  


### <span style="font-size:1.3em;"> **Positivity Rate |** </span> <br> <span style="font-size:0.9em;"> What share of tests comes back positive each day? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(mys, select = c(date, positive_rate) )

names(data)[2] <- c("Positivity rate")

data[,2] <- data[,2] * 100

# convert data frame into xts format
data <- xts(data[,2], order.by = data$date)         

col<-brewer.pal(9, 'Reds')[8]

# Plot!
config_hc(data, 
          'area', 
          'Positivity rate', 
          col[1], 
          '%')
```

*** 
<span style="text-decoration:underline; font-size:0.9em;">  *Latest data provided on `r tests_7day_date_formatted`* </span> 

<span style="font-size:1.5em; color:`r pos_rate_col`;"> **`r latest_pos_rate` %** </span>  
<span style="color:grey;"> *Daily positivity rate.* </span>   

<span style="font-size:1.5em; color:`r pos_rate_col`;"> **`r pos_rate_7day` %** </span>  
<span style="color:grey;"> *7-day moving average of positivity rate.* </span>

&nbsp;  
<span style="color: Grey;"> *Positivity rate is equal to the number of positive tests, i.e., tests that come back positive, divided by the total number of tests conducted (PCR & antigen rapid tests) within the past 24 hours. [As a general rule of thumb](https://www.jhsph.edu/covid-19/articles/covid-19-testing-understanding-the-percent-positive.html), positivity rate of **less than 5%** means there's an adequate level of testing relative to the size of the outbreak, or the epidemic is under control in a country.* </span>


### <span style="font-size:1.3em;"> **Cumulative Cases |** </span> <br> <span style="font-size:0.9em;"> How many cases have been confirmed so far? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(mys, select = c(date, total_cases) )

names(data)[2] <- c("Cumulative cases")

data[,2] <- data[,2]

data$`Cumulative cases` <- round(data$`Cumulative cases` / 1e3, 0)

# convert data frame into xts format
data <- xts(data[,2], order.by = data$date)         

col<-brewer.pal(9, 'Oranges')[4]
# Plot!

config_hc(data, 
          'area', 
          'Cumulative cases', 
          col[1], 
          'k')
```

***
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_date`* </span>   

<span style="font-size:1.5em; color:`r cumul_cases_col`;"> **`r cumul_cases`** </span>  
<span style="color:grey;"> *Cumulative number of cases.* </span>

<span style="font-size:1.5em; color:`r cumul_cases_col`;"> **`r cumul_cases_per_mil`** </span>  
<span style="color:grey;"> *reported cases per million population.* </span>



Deaths {.storyboard data-icon="fa-skull"}
=========================================

### <span style="font-size:1.3em;"> **Daily Deaths |** </span> <br> <span style="font-size:0.9em;"> What is the daily number of reported deaths? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(mys, select = c(date, new_deaths, new_deaths_smoothed) )

names(data)[c(2, 3)] <- c('Daily deaths', '7-day avg')

data$`7-day avg` <- round(data$`7-day avg`, 0)

# convert data frame into xts format
data <- xts(data[ ,c(2, 3) ], order.by = data$date)         

col <- brewer.pal(9, 'Reds')[ c(3, 9) ]

# Plot!
config_hc(data$`Daily deaths`, 
          'area', 
          'Daily deaths', 
          col[1], 
          '')                           %>%
  
hc_add_series(data$`7-day avg`, 
              type = 'spline', 
              name = '7-day avg', 
              color = col[2])
```

***
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_date`* </span>   

<span style="font-size:1.5em; color:`r death_col`;"> **+`r new_deaths`** </span>  
<span style="color:grey;"> *deaths were reported in the past 24 hours.* </span>


### <span style="font-size:1.3em;"> **Case Fatality Ratio (CFR) |** </span> <br> <span style="font-size:0.9em;"> What is the ratio between confirmed deaths and confirmed cases? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
cfr$date <- as.Date(cfr$date)
# compute CFR
data <- subset(cfr, select = c(date, cfr) )

data$cfr <- round(data$cfr, 2)

# convert data frame into xts format
data <- xts(data[,2], order.by = data$date) 

col <- brewer.pal(8, 'Dark2')[7]

# Plot!
config_hc(data, 
          'spline', 
          'CFR', 
          col[1], 
          '%')
```

***
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_date`* </span>   

<span style="font-size:1.5em; color:`r col`;"> **`r latest_cfr` %** </span>  
<span style="color:grey;"> *Case Fatality Ratio (CFR) or more commonly known as Case Fatality Rate.* </span>  
&nbsp;  

<span style="color: Grey;"> *[CFR](https://www.who.int/news-room/commentaries/detail/estimating-mortality-from-covid-19) is a commonly used measure of mortality from a disease. It is just the total number of deaths divided by the total number of confirmed cases. Careful interpretation is warranted owing to a number of important limitations in CFR — especially during a fast-moving pandemic. Read [here](https://ourworldindata.org/covid-mortality-risk) for instance.* </span>


### <span style="font-size:1.3em;"> **Cumulative Deaths |** </span> <br> <span style="font-size:0.9em;"> How many deaths have been reported so far? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
data <- subset(mys, select = c(date, total_deaths) )

# convert data frame into xts format
data <- xts(data[,2], order.by = data$date)         

col <- brewer.pal(9, 'Greys')[7]

# Plot!
config_hc(data, 
          'area', 
          'Cumulative deaths', 
          col[1], 
          '')
```

***
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_date`* </span> 

<span style="color:`r cumul_deaths_col`; font-size:1.5em;">**`r cumul_deaths`**</span>  
<span style="color:grey;"> *Cumulative number of deaths.* </span>  

<span style="font-size:1.5em; color:`r cumul_deaths_col`;"> **`r cumul_deaths_per_mil`** </span>  
<span style="color:grey;"> *reported deaths per million population.* </span>



Vaccinations {.storyboard data-icon="fa-syringe"}
=========================================

### <span style="font-size:1.3em;"> **Daily New Doses |** </span> <br> <span style="font-size:0.9em;"> How many doses are administered each day? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# compute total daily doses
for(i in 1:nrow(daily_dose) ) {
                              daily_dose$total[i] <- 
                              daily_dose$dose1[i] + daily_dose$dose2[i]
                              }

# configure data frame for highcharter  
data <- subset(daily_dose, select = c(date, dose1, dose2, total) 
               )

names(data)[ 2:4 ] <- c("1st dose", "2nd dose", 'total')

# convert data frame into xts format
data <- xts(data[, 2:4], order.by = data$date)         

# col [1] for total; col[2] for 1st dose; col[3] for 2nd dose
col <- brewer.pal(9, 'Greens')[ c(2, 6, 8) ]

# Plot!
config_hc(data$total, 
          'area', 
          'Total', 
          col[1], 
          '')                            %>%
  
hc_add_series(data$`1st dose`, 
              type = 'column', 
              color = col[2], 
              name = '1st dose')         %>%
  
  hc_add_series(data$`2nd dose`, 
                type = "column", 
                name = '2nd dose', 
                color = col[3])  
```

*** 
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_dose_date`* </span>   

<span style="font-size:1.5em; color:`r col[2]`;"> **+`r latest_dose1_formatted`** </span> &nbsp; | &nbsp;
<span style="font-size:1em; color:`r col[2]`;"> **+`r dose1_7day_avg_formatted`**</span>  
<span style="color:grey;"> *new 1st doses were administered in the past 24 hours.* &nbsp; | &nbsp; *7-day average.* </span>

<span style="font-size:1.5em; color:`r col[3]`;"> **+`r latest_dose2_formatted`** </span> &nbsp; | &nbsp;
<span style="font-size:1em; color:`r col[3]`;"> **+`r dose2_7day_avg_formatted`**</span>  
<span style="color:grey;"> *new 2nd doses were administered in the past 24 hours.* &nbsp; | &nbsp; *7-day average.* </span>


### <span style="font-size:1.3em;"> **Percentage Vaccinated |** </span> <br> <span style="font-size:0.9em;"> What share of the 32.7 million [population](https://www.dosm.gov.my/v1/index.php?r=column/cthemeByCat&cat=155&bul_id=OVByWjg5YkQ3MWFZRTN5bDJiaEVhZz09&menu_id=L0pheU43NWJwRWVSZklWdzQ4TlhUUT09) has been vaccinated? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(d, select = c(date, people_vaccinated, people_fully_vaccinated) )

data$people_vaccinated <- round( (data$people_vaccinated/32.7e6) * 100, digits = 2)

data$people_fully_vaccinated <- round( (data$people_fully_vaccinated/32.7e6) * 100, digits = 2)

names(data)[c(2, 3)] <- c("1st dose", "2nd dose")

# convert data frame into xts format
data <- xts(data[, 2:3], order.by = data$date)         

# col [1] for 2 doses [2] for 1 dose
col <- brewer.pal(9, 'Greens')[ c(5, 8) ]

# Plot!
config_hc(data$`1st dose`,  
          'area',
          '1st dose', 
          col[1], 
          '%')                    %>%

hc_add_series(data$`2nd dose`, 
              type = "area", 
              name = '2nd dose', 
              color = col[2])
```

*** 
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_dose_date`* </span>   

<span style="font-size:1.5em; color:`r col[1]`;"> **`r perc_cumul_dose1`%** </span> &nbsp;
<span style="font-size:0.9em; color:`r col[1]`;"> **+`r perc_daily_dose1`%** </span>
<span style="font-size:0.8em; color:grey;"> *from `r format( tail(d$date, 1) - 1, '%d %b')`* </span>  
<span style="color:grey;"> *have received at least 1 dose of a vaccine.* </span>  

<span style="font-size:1.5em; color:`r col[2]`;"> **`r perc_cumul_dose2`%** </span> &nbsp;
<span style="font-size:0.9em; color:`r col[2]`;"> **+`r perc_daily_dose2`%** </span>
<span style="font-size:0.8em; color:grey;"> *from `r format( tail(d$date, 1) - 1, '%d %b')`* </span>  
<span style="color:grey;"> *have received at least 2 doses of a vaccine.* </span> 



### <span style="font-size:1.3em;"> **Percentage (rounded) Vaccinated |** </span> <br> <span style="font-size:0.9em;"> Square plots </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
plot_square(dataset = target, 
            rows = c(1, 3, 5), 
            color = col[1] )   %>%
hc_title( text = 'At least 1 dose')
```

***
```{r echo=FALSE}
plot_square(dataset = target, 
            rows = c(2, 4, 5), 
            color = col[2] )        %>%
  
hc_title( text = 'Fully vaccinated') %>%
hc_legend( enabled = FALSE)
```



### <span style="font-size:1.3em;"> **Cumulative Doses |** </span> <br> <span style="font-size:0.9em;"> How many doses have been administered so far? </span>
```{r echo=FALSE, fig.height=5.5, fig.width=7, warning=FALSE}
# configure data frame for highcharter
data <- subset(d, select = c(date, people_vaccinated, people_fully_vaccinated) )

names(data)[ c(2, 3) ] <- c("1st dose", "2nd dose")

data$`1st dose` <- round(data$`1st dose` / 1e6, digits = 2)
data$`2nd dose` <- round(data$`2nd dose` / 1e6, digits = 2)

# convert data frame into xts format
data <- xts(data[, 2:3], order.by = data$date)  

# col [1] for 2 doses [2] for 1 dose
col<-brewer.pal(9, 'Blues')[ c(5, 9) ]

# Plot!
config_hc(data$`1st dose`,  
          'area', 
          '1st dose', 
          col[1], 
          'M')                        %>%

hc_add_series(data$`2nd dose`, 
              type = "area", 
              name = '2nd dose', 
              color = col[2])
```

*** 
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_dose_date`* </span>  

<span style="font-size:1.5em; color:`r col[1]`;"> **`r cumul_dose1_formatted`** </span>  
<span style="color:grey;"> *1st doses have been administered.* </span>

<span style="font-size:1.5em; color:`r col[2]`;"> **`r cumul_dose2_formatted`** </span>  
<span style="color:grey;"> *2nd doses have been administered.* </span>  
&nbsp;  
<span style="color: grey;"> Vaccine portfolio: Pfizer-BioNTech, Sinovac, Oxford-AstraZeneca </span>


### <span style="font-size:1.3em;"> **Progress Tracker |** </span> <br> <span style="font-size:0.9em;"> Is the vaccination programme on track? </span>
```{r echo=FALSE, fig.height=6, fig.width=7, warning=FALSE}
# Plot!
plot_progress_tracker

# col[1] for 1st dose; col[2] for 2nd dose
col <- brewer.pal(9, 'Greens')[ c(5, 8) ]
```

*** 
<span style="text-decoration:underline; font-size:0.9em;"> *Latest data provided on `r latest_dose_date`* </span>   

<span style="font-size:1.5em; color:`r col[1]`;"> **`r dose1_required`** </span> <span style="color:grey;"> *first doses* </span>  

<span style="font-size:1.5em; color:`r col[2]`;"> **`r dose2_required`** </span> <span style="color:grey;"> *second doses* </span>  

<span style="color:grey;"> *required **each day on average** over the next **`r dayleft`** days to achieve Phase 2 target.* </span>  
&nbsp;  
<span style="color: Grey;"> *[The government aims](https://www.vaksincovid.gov.my/pdf/Program_Imunisasi_COVID-19_Kebangsaan_Versi_Bahasa_Inggeris.pdf) to inoculate at least 23.6 million people (72.2% of population) against COVID-19 by February 2022. Phase 1, 2 & 3 involve 0.5m, 9.4m & at least 13.7m people, respectively. Each shaded region corresponds to the month within which each phase is targeted to be completed.* </span>



Comparisons {.storyboard data-icon="fa-globe-asia"}
=========================================

### <span style="font-size:1.3em;"> **New cases per million | Choropleth map ** </span>
```{r echo=FALSE, fig.height=6, fig.width=7, warning=FALSE}
# Plot map (new cases per million)
plot_map_cases_per_million(dataset = mapdata,
                           mapsource = "custom/world-highres")
```

***
How do we compare to other countries in terms of daily number of cases per million population? Hover your cursor over or tap a country of interest to see the data corresponding to that country. You can zoom in and out of the map using the zoom buttons or pinch  on the touch screen with two fingers if you are using a touch device. Panning will be enabled when the map is zoomed in.


### <span style="font-size:1.3em;"> **New cases per million | Bubble plot ** </span>
```{r echo=FALSE, fig.height=6, fig.width=7, warning=FALSE}
plot_bubble_cases
```

***
All countries are grouped (colour-coded) by continents, except Malaysia where it is represented by a unique colour. Each bubble represents a country, with its radius corresponding to the size of that country. Hover your cursor over or tap the bubbles to explore the number of daily cases per million population in different countries. If you are using a computer, you can highlight a continent by hovering your cursor over the legend text (at the bottom of the plot) associated with that continent. To deselect a continent, click or tap on the legend text. (you can therefore zoom in on a continent of interest by deselecting all other continents). Note that the y-axis is log-scaled.


### <span style="font-size:1.3em;"> **Fully vaccinated | Choropleth map ** </span>
```{r echo=FALSE, fig.height=6, fig.width=7, warning=FALSE}
# Plot map (new cases per million)
plot_map_vac_per_hundred(dataset = vac_data,
                           mapsource = "custom/world-highres")
```

***
Where do we stand globally in terms of the percentage of population fully vaccinated against COVID-19? Hover your cursor over or tap a country of interest to see the data corresponding to that country. Remember you can zoom in and out of the map. Panning will be enabled when the map is zoomed in.


### <span style="font-size:1.3em;"> **Fully vaccinated | Bubble plot ** </span>
```{r echo=FALSE, fig.height=6, fig.width=7, warning=FALSE}
plot_bubble_vac
```

***
All countries are grouped (colour-coded) by continents, except Malaysia where it is represented by a unique colour. Each bubble represents a country, with its radius corresponding to the size of that country. Hover your cursor over or tap the bubbles to explore the percentage of population fully vaccinated in different countries. If you are using a computer, you can highlight a continent by hovering your cursor over the legend text (at the bottom of the plot) associated with that continent To deselect a continent, click or tap on the legend text (you can therefore zoom in on a continent of interest by deselecting all other continents). Note that the y-axis is log-scaled.

